A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories

### 2016-10-28 Camera-Ready/sec1_introduction.tex
Camera-Ready
Ohohoho

\section{Introduction}
The prevalence of positioning devices has drastically boosted 
the scale and spectrum of trajectory collection to an unprecedented level. 
Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
records, are continually generated from animal telemetry chips, 
vehicle GPSs and wearable devices. Data analysis on large-scale 
trajectories benefits a wide range of applications and services, 
including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, and social recommendations~\cite{bao2013survey}, to name just a few.

@@

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
with different constraints with respect to clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised approach by allowing
arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns. The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

\vspace{-2mm}
Figure~\ref{fig:related_work} is an example to demonstrate the concepts of the various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering method as a blackbox and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  are the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
\vspace{-0.5em}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
}
\vspace{-0.5em}
\label{fig:platoon_weakpoint}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\vspace{-0.5em}
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\vspace{-0.5em}
\label{tbl:existing_co_patterns}
\end{table}

@@

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
            \vspace{-1.5em}
		\subcaption{ Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
            \vspace{-1.5em}
         \subcaption{ Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
   \vspace{-0.5em}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
    \vspace{-0.5em}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we design a baseline solution by replicating the snapshots in multiple data chunks to support effective parallel mining. Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. SPARE achieves workload balance by partitioning objects into fine granular stars.  For each star partition, an Apriori Enumerator is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

@@

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution named \emph{Temporal Replication and Parallel Mining} (TRPM). An advanced solution named
\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions. Finally, Section~\ref{sec:concl} concludes the paper.

>>>>

\section{Introduction}
The prevalence of positioning devices has drastically boosted 
the scale and spectrum of trajectory collection to an unprecedented level. 
Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
records, are continually generated from animal telemetry chips, 
vehicle GPSs and wearable devices. Data analysis on large-scale 
trajectories benefits a wide range of applications and services, 
including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, location-aware advertising~\cite{guo2016influence},  and social recommendations~\cite{bao2013survey}, to name just a few.

@@

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
with different constraints with respect to clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}%~\cite{gudmundsson2006flock} 
and the \emph{convoy}%~\cite{jeung2008convoy} 
require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}%~\cite{li2010swarm}
does not impose any restriction. 
The \emph{group}%~\cite{wang2006grouppattern} 
and the \emph{platoon}%~\cite{li2015platoon} 
adopt a compromised approach by allowing
arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

\begin{figure}[h]
\centering
\includegraphics[width=0.40\textwidth]{related_work.eps}
%\vspace{-0.5em}
\caption{Trajectories and co-movement patterns. The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
%\vspace{-0.5em}
\label{fig:related_work}
\end{figure}

Figure~\ref{fig:related_work} is an example to demonstrate the concepts of the various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering method as a blackbox and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  are the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
%\vspace{-0.5em}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2\rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
}
%%\vspace{-0.5em}
\label{fig:platoon_weakpoint}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.7cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Conse-cutiveness}} & { \textbf{Time Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2006flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
%%\vspace{-0.5em}
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
%\vspace{-0.5em}
\label{tbl:existing_co_patterns}
\end{table}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{ Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{ Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    %\vspace{-0.5em}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    %\vspace{-0.5em}
    \label{fig:related_work_scalability}
\end{figure}

@@

Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we design a baseline solution by replicating the snapshots 
%in multiple data chunks 
to support effective parallel mining. 
Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. 
SPARE achieves workload balance by partitioning objects into fine granular stars. 
For each partition, an Apriori Enumerator is adopted to mine the co-movement patterns. 
Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

@@

%The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
%trajectory pattern mining. Section~\ref{sec:definition} states the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline %solution named \emph{Temporal Replication and Parallel %Mining} (TRPM). An advanced solution named
%\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions. Finally, Section~\ref{sec:concl} concludes the paper.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes related work. Section~\ref{sec:definition} states the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline 
solution. % named \emph{Temporal Replication and Parallel Mining} (TRPM).
An advanced solution named
\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} reports our experimental evaluation.
Finally, Section~\ref{sec:concl} concludes the paper.

### 2016-10-28 Camera-Ready/sec3_definitions.tex
Camera-Ready
Ohohoho

\begin{table}[h]
\vspace{-2mm}
\centering
\begin{tabular}{|c|p{6.5cm}|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\vspace{-0.5em}
\caption{Operators on time sequence.}
\vspace{-0.5em}
\label{tbl:operators}
\end{table}

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose-connection} anomaly. 
To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$, i.e.,
 $\forall i \in (1,\ldots,|T|-1), T[i+1]-T[i] \leq G$.
\end{definition}

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
%parameters to users to accommodate various application needs.}  
By customizing these parameters, our pattern can 
express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose-connection} anomaly by tuning the parameter $G$. 
%It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
\hline 
\end{tabular} 
   \vspace{-0.5em}
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
% $M$ represents the  \emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.
}
    \vspace{-0.5em}
\label{tbl:patterns}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
%$\Gamma$ & size of the largest star partition\\
%\hline
\end{tabular} 
\vspace{-0.5em}
\caption{Summary of notations.}
\vspace{-0.5em}
\end{table}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{|c|p{6.5cm}|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
%\vspace{-0.5em}
\caption{Operators on time sequence.}
%\vspace{-0.5em}
\label{tbl:operators}
\end{table}

We say a sequence $T$ is consecutive 
if $\forall 1 \leq i < |T|, T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose-connection} anomaly. 
To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-con-nected if the gap between any of its neighboring timestamps is no greater than $G$, i.e., $\forall 1 \leq i < |T|, T[i+1]-T[i] \leq G$.
\end{definition}

@@

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in every timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
%parameters to users to accommodate various application needs.}  
By customizing these parameters, our pattern can 
express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose-connection} anomaly by tuning the parameter $G$. 
%It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
\hline 
\end{tabular} 
%\vspace{-0.5em}
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.}
%\vspace{-0.5em}
\label{tbl:patterns}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
%$\Gamma$ & size of the largest star partition\\
%\hline
\end{tabular} 
%\vspace{-0.5em}
\caption{Summary of notations.}
%\vspace{-0.5em}
\end{table}
